Viscous Transport in Eroding Porous Media

### 2019-06-11 docs/transport/erosion_transport.tex
do the result section in transport paper

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
\caption{\label{fig:Eroding20tort_traj} The largest 20 difference of the length of 
two neighbor tracers' trajectories in
 20 nearly touching bodies eroding}
\end{figure}

>>>>

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of the length of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}
